\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-04-15 investigation/docs/overview.tex
edits to the report doc and scripts for the analysis

\newpage
\begin{figure}[H]
\centering
\includegraphics[width=4in]{lambda.png}
\caption*{Figure | Distribution of median lambda from the 501 fixed SNP analysis. Red denotes original pairs identified from filter 2 - i.e. no previous study-wide additive effects. Black denotes the original filter 1 pairs}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
probename & snp1 & snp2 & meanlambda & npairs \\ 
  \hline
ILMN\_1704730 & rs1884655 & rs10255470 & 2.88 & 10 \\ 
ILMN\_1710752 & rs2123758 & rs2786014 & 2.15 & 8 \\ 
ILMN\_1717234 & rs1157079 & rs7733671 & 4.31 & 17 \\ 
ILMN\_1720059 & rs12435486 & rs7837237 & 2.29 & 7 \\ 
ILMN\_1738784 & rs10930170 & rs12120009 & 2.24 & 6 \\ 
ILMN\_1755589 & rs11080134 & rs11169322 & 1.16 & 6 \\ 
ILMN\_1786426 & rs2839013 & rs8106959 & 5.65 & 20 \\ 
ILMN\_1804396 & rs1293455 & rs2655991 & 1.38 & 7 \\ 
ILMN\_2313158 & rs10869600 & rs13069559 & 3.15 & 15 \\ 
ILMN\_2372639 & rs17159840 & rs10059004 & 4.17 & 17 \\ 
ILMN\_3231952 & rs12947580 & rs8079215 & 2.16 & 6 \\ 
   \hline
\end{tabular}
\caption*{Mean lambda per probe, when 5 or more interactions are identified amongst the 501 pairs}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[height=3in]{empF.png}
\caption*{Figure | The F-statistic corresponding to $p=4.48^{-6}$ and df1=4, df2=842 from a $H_0$ table is 7.67. This figure shows the empirical (ranked) F-statistic corresponding to $n * 4.48^{-6}$. Where $n * 4.48^{-6} < 1$, the largest F-statistic taken. There are 96 pairs where the corresponding F statistic is less than 7.67}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[height=3in]{Npairs_above_empthres.png}
\caption*{Figure | For each pair (n=501) the number of tests where the test statistic is greater than the 95th percentile of an F-dist}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=3in]{type1.png}
\caption*{Figure | Distribution of the empirical type 1 error rate. Determined as the proportion of tests with $F > 2.38$ (95th percentile of F-dist with df1=4, df2=842)}
\end{figure}

>>>>

\newpage
\begin{figure}[H]
\centering
\includegraphics[width=3in]{lambdaF1.png}
\caption*{Figure | Distribution of median lambda from the 406 filter 1 pairs from the GWAS based analysis. The mean lambda is 1.94}

\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=3in]{lambdaF2.png}
\caption*{Figure | Distribution of median lambda from the 95 filter 2 pairs from the GWAS based analysis. The mean lambda is 1.31}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
 probename & snp1 & snp2 & gene & meanlambda & npairs \\ 
  \hline
ILMN\_1704730 & rs1884655 & rs10255470 & CD93 & 2.88 & 10 \\ 
ILMN\_1710752 & rs2123758 & rs2786014 & NAPRT1 & 2.15 & 8 \\ 
ILMN\_1717234 & rs1157079 & rs7733671 & CAST & 4.31 & 17 \\ 
ILMN\_1720059 & rs12435486 & rs7837237 & HMBOX1 & 2.29 & 7 \\ 
ILMN\_1738784 & rs10930170 & rs12120009 & PPP2R5A & 2.24 & 6 \\ 
ILMN\_1755589 & rs11080134 & rs11169322 & DIP2B & 1.16 & 6 \\ 
ILMN\_1786426 & rs2839013 & rs8106959 & TMEM149 & 5.65 & 20 \\ 
ILMN\_1804396 & rs1293455 & rs2655991 & C14ORF4 & 1.38 & 7 \\ 
ILMN\_2313158 & rs10869600 & rs13069559 & MBNL1 & 3.15 & 15 \\ 
ILMN\_2372639 & rs17159840 & rs10059004 & TRAPPC5 & 4.17 & 17 \\ 
ILMN\_3231952 & rs12947580 & rs8079215 & ARL17B & 2.16 & 6 \\ 
   \hline
\end{tabular}
\caption*{Mean lambda per probe, when 5 or more interactions are identified amongst the 501 pairs}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[height=3in]{empF.png}
\caption*{Figure | The F-statistic corresponding to $p=4.48^{-6}$ and df1=4, df2=842 from a $H_0$ table is 7.67. This figure shows the empirical (ranked) F-statistic corresponding to $n * 4.48^{-6}$. Where $n * 4.48^{-6} < 1$, the largest F-statistic is taken. There are 96 pairs where the corresponding F statistic is less than 7.67}. None of these are amongst the 30 bonferroni correction significant pairs.
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[height=3in]{Npairs_above_empthres.png}
\caption*{Figure | For each pair (\emph{n}=501) the number of tests where the test statistic is greater than the 95th percentile of an F-dist}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=3in]{type1.png}
\caption*{Figure | Distribution of the empirical type 1 error rate. Determined as the proportion of tests with $F > 2.38$ (95th percentile of \emph{F}-dist with df1=4, df2=842)}
\end{figure}
